Correlation tests

### 2025-04-16 analysis/manuscript.tex
Add basic usage notes

% Change \title, \date, remove \author:
\begin{large}
\textbf{Estimating transformative agreement impact on hybrid open access: A comparative large-scale study using open metadata, Scopus and Web of Science}
\end{large}

>>>>

% Change \title, \date, remove \author:
\begin{large}
\textbf{Estimating transformative agreement impact on hybrid open access: A comparative large-scale study using Scopus, Web of Science and open metadata}
\end{large}
